\Huge Conferences in an Era of Expensive Carbon

### 2019-06-18 main.tex
Fleshed out further.

Publicly accounting for CO2e expenditures will incentivize eliminating
CO2e-consuming activities whose corresponding value to the conference
is likely to be low. But a public accounting is unlikely to
incentivize major CO2e reductions, since these will require
significant changes to conference system itself, which may negatively
impact the value that conferences provide. 
%
Science is a fundamentally social process, and the conference system
accelerates research through high-bandwidth interaction, direct
dissemination of results, network building, and serendipitous
cross-fertilization.
%
Organizers and attendees will be reticent to harm the scientific
benefits they have all regularly experienced.

(Mike: I think we can significantly trim the text below. Instead, we can
talk here about a carbon tax as the next natural step. It can be
related to the sugar tax that some municipalities have imposed; when
public calorie counts are not enough to discourage use, add a tax
instead. The arc from the bullet list can come earlier, basically.)

Thus we have the question of apples and oranges: How can we weigh the
environmental harm caused by conference travel against the social
benefits of the scientific progress that comes from conferences?

% The question is difficult because the harm and
% the compensating benefits cannot be easily compared---they are apples and
% oranges.

Fortunately, we have a well-established mechanism for comparing apples and
oranges---indeed, for comparing almost anything!  Economists call it ``the
magic of markets.''  By mapping choices and preferences in disparate domains
onto a common scale (i.e., money), economic markets function as massively
distributed computations that optimize costs and benefits across vastly
different activities.\bcp{Give a simple, concrete example.}  For this
reason, many policy experts advocate addressing climate change through some
form of carbon pricing, which places a monetary cost on greenhouse gas
emissions, sending a clear market signal that changes aggregate
behavior.\bcp{See
  https://kleinmanenergy.upenn.edu/policy-digests/why-carbon-pricing-falls-short
  for lots of good phrasing and citations.}

  \begin{itemize}
  \item To motivate more painful changes and force people to make difficult
  choices, we need a price on carbon.
  \item Ultimately, governments should do this.  But we don't need to wait:
  as several companies have shown, even an artificial ``internal price'' on
  carbon creates a significant price signal that shapes behavior.
  \item Our second (more ambitious) proposal is: ACM should begin requiring
  conferences to pay a surcharge based on their carbon footprint.  It should
  be low at the beginning and increase steadily (and predictably) year on year.
  \item Benefit: This will create concrete downward pressure on conferences
  to decrease their footprints.  They can then choose (on the basis of
  careful analysis of data and weighing of benefits) how best to do so.
\item The money raised in this way can be used in many ways: buying
  carbon offsets (Mike: could include text from below on this),
  supporting ``green computing research'', virtualizing conferences
  (livestreaming, etc.), supporting a transition to a low-carbon / few
  conferences business model for ACM.
  \end{itemize}

(Mike: Need to include somewhere above:)

However, going beyond these simple steps is going to be much more
challenging.  One reason is that it isn't actually very clear what changes
will help significantly.  (Describe some of our data.  Show the two
diagrams.  Draw some conclusions / discuss why it's hard to draw
conclusions.)  More data and more thorough analysis is needed.

>>>>

Publicly accounting for CO2e expenditures will incentivize some CO2e
reductions, but probably not major changes to conference system
itself, since doing so may negatively impact the value that
conferences provide.
%
Science is a fundamentally social process, and the conference system
accelerates scientific research through high-bandwidth interaction,
direct dissemination of results, network building, and serendipitous
cross-fertilization.
%
Organizers and attendees will be reticent to make changes that could
harm the scientific benefits they have all regularly experienced.
%
Nevertheless, it seems clear that the status quo is unsustainable, so
hard choices will have to be made. How to motivate organizers to make
them?

This dilemma is the one that all of society faces, in a microcosm. To
address it, many policy experts advocate some form of carbon tax (or
\emph{price}), which adds a near-term, monetary cost to greenhouse gas
emissions~\cite{carbonprice}. Doing so makes manifest today the hidden
environmental cost of CO2e emissions on tomorrow, thus incentivizing
CO2e-reducing changes without specifying exactly which, thus allowing
for creative and efficient responses. As an analogy, some
municipalities such as New York city and Philadelphia have imposed a
per-calorie tax on soft drinks, with some studies finding that doing
so indeed reduced consumption~\cite{sodatax}.

In the best case, governments would impose a CO2e tax uniformly, and
all CO2e-intensive activities would have to pay it. But ACM could send
a strong message about the importance of this issue by acting now. In
particular, as several companies have shown, even an artificial ``internal price'' on
  carbon creates a significant price signal that shapes behavior.
%
  Thus, our second (more ambitious) proposal is: ACM should begin requiring
  conferences to pay a surcharge based on their carbon footprint.  It should
  be low at the beginning and increase steadily (and predictably) year
  on year.
%
Conference organizers can choose (on the basis of
  careful analysis of data and weighing of benefits) how best to do
  so.

 What should ACM do with the funds collected? The money raised in
  this way can be used in many ways: buying carbon offsets, supporting
  ``green computing research'', virtualizing conferences
  (livestreaming, etc.), supporting a transition to a low-carbon / few
  conferences business model for ACM.

Once again, ACM should provide support to conference organizers to
prepare for a future of higher-cost conferences.

(Mike: Here we can talk about data analysis, and how it could provide
help with this. We've started, and see that the situation is not very
clear. Describe some of our data.  Show the two diagrams.  Draw some
conclusions / discuss why it's hard to draw conclusions.

\SECTION{Conclusion}
